### 2023-02-09 article3.qmd
update

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  if(length(check_colour) == 3){ # there is at least a negative jump
    index_neg_jump <- which(tmp2$colour == 'negative jump')
    tmp2 <- tmp2[-c(index_neg_jump, index_neg_jump+1),]
    tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else if(length(check_colour) == 2){ # only positive jumps
    tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

@@

@@

>>>>

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  # if(length(check_colour) == 3){ # there is at least a negative jump
  #   index_neg_jump <- which(tmp2$colour == 'negative jump')
  #   tmp2 <- tmp2[-c(index_neg_jump, index_neg_jump+1),]
  #   tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
  #   even_indexes <- seq(2,nrow(tmp2),2)
  #   tmp2 <- tmp2[even_indexes,]
  # }else if(length(check_colour) == 2){ # only positive jumps
  #   tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
  #   even_indexes <- seq(2,nrow(tmp2),2)
  #   tmp2 <- tmp2[even_indexes,]
  # }else{ # No jump
  #   tmp2 <- NULL
  # }
  if(length(check_colour) >= 2){ # there is a least a jump (positive or negative)
    tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

@@

```{r, get jump info}

get_jump_info <- function(data){

  # remove negative jumps, if any
  check_colour <- unique(tmp2$colour)
  if(length(check_colour) >= 2){ # there is a least a jump (positive or negative)
    tmp2 <- tmp2 |> mutate(diff_jump = cp - lag(cp)) 
    even_indexes <- seq(2,nrow(tmp2),2)
    tmp2 <- tmp2[even_indexes,]
  }else{ # No jump
    tmp2 <- NULL
  }

  if(is.null(tmp2)){ # no jump
    big_part_poc_flux <- 0
    tmp3 <- NULL
  }else{
    tmp3 <- tmp2 |> filter(diff_jump > 0) # remove negative
    if(nrow(tmp3) == 0){ # no positive jumps
      big_part_poc_flux <- 0
    }else{
      delta_y <- sum(tmp3$diff_jump) *0.25 # to get ATN (= cp*0.25)
      max_time <- max(tmp$dates)
      min_time <- min(tmp$dates)
      delta_x <- as.numeric(difftime(max_time, min_time, units = 'days'))
      slope_big_part <- delta_y/delta_x
      big_part_poc_flux <- 633*(slope_big_part**0.77)
    }
  }

  # plot
  # jump_plot <- plot_ly(tmp, x = ~dates, y = ~cp, type = 'scatter', mode = 'markers', color = ~colour, colors = c('#003366','#E31B23', '#FFC325')) |>
  #   add_lines(data= part_slope_tmp, x = ~dates, y = ~cp, split = ~group, color = I('#DCEEF3'), showlegend = F) |>
  #   layout(title= paste0('Drifting time: ', round(drifting_time,3), ' days\n',
  #                        'Mean ATN slope (light blue): ', round(mean_slope,3), ' day-1\n',
  #                        'POC flux (small particles): ', round(poc_flux,1), ' mg C m-2 day-1\n',
  #                        'POC flux (big particles): ', round(big_part_poc_flux,1), ' mg C m-2 day-1'), yaxis = list(title = 'Cp (1/m)'), xaxis = list(title = 'Time'))

  # clean data to send
  slope_df <- slope_df |> arrange(min_time) |> mutate(min_drifting_time = df$min_time, max_drifting_time = df$max_time, small_flux = df$small_flux, big_flux = df$big_flux, park_depth = data$park_depth[1], wmo = data$wmo[1],cycle = data$cycle[1])
  if(is.null(tmp3)){
    big_jump <- tmp3
  }else{
     big_jump <- tmp3 |> mutate(park_depth = data$park_depth[1], wmo = data$wmo[1],cycle = data$cycle[1]) 
  }

  return(list(slope_info = slope_df, jump_info = big_jump))
}
```

TO DO HERE

```{r, compute slope and jump info}

# i <- 4903634
# j <- '1000 m'
# k <- 15
# tmp <- all_floats_slope |> filter(wmo == i, park_depth == j, cycle == k)
# 
# data <- tmp

res_slope <- data.frame()
res_jumps <- data.frame()
for (i in wmo){
  max_cycle <- as.numeric(all_floats_slope |> filter(wmo == i) |> dplyr::summarise(max_cycle = max(cycle)))
  for (j in park_depth){
    for (k in seq(1:max_cycle)){
      tmp <- all_floats_slope |> filter(wmo == i, park_depth == j, cycle == k)
      if(nrow(tmp) == 0){
        next
      }else if(nrow(tmp) < 3){ # case where there is not enough data
        next
      }else{
          output <- get_jump_info(tmp)
          res_slope <- rbind(res_slope, output$slope_info)
          res_jumps <- rbind(res_jumps, output$jump_info)
      }
    }
  }
}

@@

```{r, check gaussian profiles}

# depth layers for Gaussian fit
depthL <- c(seq(40,200,20), c(250,300,400,500,600,800,1000,1250,1500,1750,2000))

# Gaussian formula #> but z is not the depth but the TIME
fgauss <- function(z, peak_conc, peak_doy, dz){
  peak_conc*exp(-((z-peak_doy)**2)/(dz**2))
}

return_fitted <- function(d){

  #timeframe near the bloom so to say
  ztime <- seq(160,240,1)
  # gaussian fit
  tib <- map_dfr(1:nrow(d), function(i){tibble(ztime = ztime, fgauss = fgauss(ztime, d$max_abundance[i], d$time_max_abundance[i], d$standard_dev[i]), depth = d$depth[i])})
  return(tib)
}

# test
tmp <- sinking_fit |> filter(wmo == 6904240, size == 645)

test <- return_fitted(tmp)

ggplot(test, aes(x = ztime, y = fgauss, colour = factor(depth))) + geom_point() + theme_bw() #+ ylim(c(0,.2))
